
\section{Customer Discovery\label{methodology:customerDiscovery}}

Customer discovery, interviewing and shadowing potential product end-users, is an important component of early-stage device design. This allows the research team to verify and refine the device needs and requirements before dedicating time and resources towards research and development.

\subsection{Lumpectomy Observations\label{sec:methodology:customerDiscovery:lumpectomyObservations}}

Through a collaboration with OSUCCC, the research team was able to shadow multiple lumpectomy procedures. This allowed the team to see first-hand how competitor devices are used and better understand the pain points and potential opportunities for improvement in the tumor marking process.

Discussion of key findings from lumpectomy observations can be found in~\fullref{sec:discussion:customerDiscovery:lumpectomyObservation}.

\subsection{Interviews\label{sec:methodology:customerDiscovery:interviews}}

Multiple interviews were also conducted with surgical oncologists across multiple hospitals. These were initiated through connections across The Ohio State University Medical Center.

\subsubsection{Interview Guide and Notes Template\label{sec:methodology:customerDiscovery:interviews:guideAndNotes}}

To standardize and better prepare for these interviews, a discussion and notes guide were created. Full size versions of these are shown in~\fullref{sec:appendix:interviewTemplates}. These guides allowed the research team to easily lead the conversations. Additionally, by making note-taking more standardized, comparisons could be drawn more easily between interviews.
